
We're going to begin by grabbing the Boston Housing Data.

From 10,000 feet, this dataset involves the median value of occupied homes in Boston, as a function of 13 covariates.

```{r}
library(MASS)
library(data.table)
library(magrittr)
data(Boston)
boston <- data.table(Boston)
head(boston)
```



```{r}
library(GGally)
ggpairs(
  boston[, .(lstat, black, ptratio, tax, medv)]
)

ggpairs(
  boston[, .(rad, dis, age, rm, crim)]
)

ggpairs(
  boston[, .(nox, chas, indus, zn, crim)]
)

```


Immediately from the kernel density estimators, some of our covariates are bimodal -- maybe some of these groups are better thought as factors?


```{r}
# Create a few new factors 
# (Remember, data.table syntax dt[i, j, by])
boston[, tax_factor := 'Low'][
       tax > 550, tax_factor := 'High']
# Now plot the new features to see if these affect any of our other covariates in interesting ways!

ggpairs(
  boston[, .(dis, age, lstat, black, ptratio, medv, tax_factor)],
  columns = c('dis', 'age', 'lstat', 'black', 'ptratio', 'medv'),
  aes(color=tax_factor)
)

# ggpairs(
#   boston[, .(rad, dis, age, rm, crim)]
# )
# 
# ggpairs(
#   boston[, .(nox, chas, indus, zn, crim)]
# )

```

Now that we've seen a few interesting things with GGally, let's move on to try some other tools:

- XGBoost + ICEbox + PDP
```{r}
library(xgboost)
xgb_mat <- data.matrix(boston[, -c('medv'), with=FALSE])
params <- list(
  objective='reg:linear',
  max_depth=9,
  gamma=.2, 
  eta=.005
)
xgb_cv <- xgb.cv(data=xgb_mat,
                 label = boston$medv,
                 nrounds=1000,
                 nfold=5,
                 early_stopping_rounds = 10)
xgb_model <- xgb.train(params, data=xgb.DMatrix(data=xgb_mat, label=boston$medv), nround=100)
```
```{r}
xgb.ggplot.importance(xgb.importance(xgb_model, feature_names = names(xgb_mat)))
```

```{r}
library(pdp)
partial = partial(xgb_model, pred.var = 'lstat', train=xgb_mat)
plot(partial$lstat, partial$yhat)
```

